\section{Problems Encountered}

The group encountered several impediments in the course of the project:

\begin{itemize}

\item \textbf{Connecting the switch to NAM}: The group encountered two problems while connecting the up-link cable from the switch to the NAM port in the wall. One of the NAM's was not configured properly, and the one that was configured for usage caused the switch to recycle power when connected to the Power Over Ethernet port on the switch. The group with the help of the Technical Director were eventually able to resolve the problem by communicating with the appropriate IET channel, and by trial and experiment.

\item \textbf{Configuring 802.1q tagging on the switch}: The next problem the group faced was with configuring the switch settings so that 802.1 tagging was enabled for the VLAN with ID 200 (the VoIP VLAN). The group initially wanted to configure the switch settings through a console cable, but upon reading the switch manual, the group concluded that the switch could only be configured through the switch software that came with it. The group installed a fresh copy of windows on our test computer and was able to install the switch software. After trial and error, the group eventually configured some ports on the switch to support 802.1q tagging.


\item \textbf{Configuring Internet Access in Lab}: After, the group had set-up the switch and the phones, the next step was to install Wireshark, a network sniffer program. But unfortunately, the group had no Internet connection on the test computer. IET helped the group register the test PC and provided an IP address. However, the IP address provided was diagonsed as a duplicate address by the Networking Interface on the test computer. After a physical visit by an IET technician, the issue was conceded and the group was provided a new IP address, and finally a working Internet connection. 

\end{itemize}